\documentclass[11pt,fleqn]{article}
\renewcommand{\baselinestretch}{1.3}
\usepackage{hyperref,harvard,amsmath,amssymb,lscape,graphicx,setspace,cancel,amsthm,color,soul,totcount,graphicx}
%\usepackage{amsfonts,latexsym,eurosym}
\bibliographystyle{aer}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Exam details
\newcommand{\course}{Econ 126: Computational Macroeconomics}
\newcommand{\term}{Winter 2020}
\newcommand{\professor}{Jenkins}
\newcommand{\examdate}{\textbf{Due: 12:30pm, March 20, 2020}}
\newcommand{\examtitle}{\textbf{Final Exam}}
\newcommand{\instructions}{Please read these instructions carefully. There are \total{pnts} points 

\EN
\item \emph{Submission}: You will submit two files. 
	\EN
	\item A .doc, .docx, or .pdf formatted file, with your answers to exam questions. This document must be well organized and easy to read.
	\item An .html version of the Jupyter Notebook file containing all code that you used to generate images and statistics for your exam. Code must be well-organized and thoroughly documented with comments explaining what your code is doing.
	\NE
	
\item \emph{Collaboration}: You may collaborate with others in the class subject to two requirements:
	\EN
	\item At the top of the exam document (the Word or pdf file), you must list the names of everyone in the class that you worked with.
	\item Everyone must prepare their own code. If any two Notebooks are deemed sufficiently similar, then the authors of both Notebooks will receive point reductions up to the entire point value of the exam. Make sure that your comments documenting the code are in your own words.
	\NE
	
\item \emph{Deadline}: Exams will not be accepted after the deadline indicated above.


\NE

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other setup commands

\pdfpagewidth 8.5in
\pdfpageheight 11in
\topmargin 0in
\headheight 0in
\headsep 0in
\textheight 9in
\textwidth 6.5in
\oddsidemargin 0in
\evensidemargin 0in
\headheight 0in
\headsep 0in

\newcommand{\D}{\displaystyle}
\newcommand{\E}{\begin{eqnarray*}}
\newcommand{\F}{\end{eqnarray*}}
\newcommand{\EE}{\begin{eqnarray}}
\newcommand{\FF}{\end{eqnarray}}
\newcommand{\IZ}{\begin{itemize}}
\newcommand{\ZI}{\end{itemize}}
\newcommand{\EN}{\begin{enumerate}}
\newcommand{\NE}{\end{enumerate}}
\newcommand{\itemc}{\item[$\circ$]}
\newcommand{\IZdash}{\begin{itemize} \renewcommand{\labelitemi}{-}}
\newcommand{\tn}{\textnormal}

\regtotcounter{pnts}

\newcounter{pnts}
\setcounter{pnts}{0}

\newcommand{\ans}{\item}
\newcommand{\cor}{\item}
\newcommand{\itemt}[1]{\item \textbf{#1}.}
\newcommand{\itemp}[1]{\item (#1 points\addtocounter{pnts}{#1})}

\newenvironment{question}[1]{\item #1\begin{singlespacing}\EN}{\NE\end{singlespacing}}
\newcommand{\bqu}{\begin{question}}
\newcommand{\equ}{\end{question}}

\makeatletter
\newcommand{\shiftleft}{\hspace*{-\@totalleftmargin}}
\newenvironment{fullwidth}
    {\par
     \setlength{\@totalleftmargin}{0pt}%
     \setlength{\linewidth}{\hsize}%
     \list{}{\setlength{\leftmargin}{0pt}}
     \item\relax}
    {\endlist}
%% colored minipage (do not break across pages!)
\newsavebox{\cminibox}
\newlength{\cminilength}
\makeatother

\newcommand{\scenario}[2]{\begin{fullwidth} \textbf{Use the following information to answer the next #1 questions.} #2  \end{fullwidth}}


\onehalfspacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\course & %Name:\rule{50mm}{.1pt}

\\
\term: \professor & %ID:\rule{50mm}{.1pt}
\end{tabular*}
\end{table}

\begin{center}
\examtitle\\
\examdate
\end{center}

\

\noindent \textbf{Instructions:} \instructions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Questions begin on the next page.

\newpage
%\textbf{Questions}


%\input{q_decentralized_rbc.tex}
\input{q_rbc_w_g.tex}
\input{q_prescott_summers.tex}
\input{q_rbc_nk.tex}

\end{document}
